\documentclass{beamer}
\usetheme{boxes}

\setbeamertemplate{navigation symbols}{}
\setbeamertemplate{itemize item}{\color{azure}$\blacksquare$}
\setbeamercolor{frametitle}{fg=azure}
\setbeamercolor{title}{fg=azure}
\setbeamercolor{framesubtitle}{fg=azure}
\setbeamercolor{block title}{fg=azure}



\usepackage{fontspec}
\setmainfont{Raleway}

\AtBeginSection[]{
  \begin{frame}
  \vfill
  \centering
  \begin{beamercolorbox}[sep=8pt,center,shadow=true,rounded=true]{title}
    \usebeamerfont{title}\insertsectionhead\par%
  \end{beamercolorbox}
  \vfill
  \end{frame}
}

\usepackage{emoji}

\usepackage{xcolor}
\definecolor{azure}{rgb}{0.0, 0.5, 1.0}
\definecolor{awesome}{rgb}{1.0, 0.13, 0.32}

\usepackage{svg}

\usepackage[
    type={CC},
    modifier={by-nc-sa},
    version={3.0},
]{doclicense}

\title[JOSS]{The Journal of Open Source Software: Developing a Software Review Community} % The short title appears at the bottom of every slide, the full title is only on the title page

\author{Patrick Diehl} 
\institute[LANL] % Your institution as it will appear on the bottom of every slide, may be shorthand to save space
{
Applied Computer Science \\ Los Alamos National Laboratory \\ Department of Physics and Astronomy \\ Louisiana State University \\ % Your institution for the title page
\medskip
\textit{diehlpk@lanl.gov} \\ % Your email address
\vspace{0.25cm}
\tiny LA-UR-24-31426
}


\begin{document}

\begin{frame}
\titlepage
\end{frame}

\begin{frame}{Motivation}

\begin{center}
    \textcolor{azure}{(Open source) software is essential for computational sciences}
\end{center}

\textbf{For example}, developing an R, C\texttt{++}, or Python package with some novel algorithms which are widely used by the research community is cool, but might not yet be considered for promotions, grant applications, or for awarding tenure. \emoji{astonished}\\
\vspace{0.25cm}
\textbf{Funding}: NSF's Pathways to Enable Open-Source Ecosystems (POSE)\footnote{\tiny\url{https://new.nsf.gov/funding/opportunities/pose-pathways-enable-open-source-ecosystems}}. \emoji{clap}\\
\vspace{0.25cm}
\textcolor{awesome}{Contrary}, people get credit for papers (citations) using open source software. How can we change that, and people get credit for software? \emoji{thinking} 
\end{frame}

\begin{frame}
\frametitle{Overview} % Table of contents slide, comment this block out to remove it
\tableofcontents % Throughout your presentation, if you choose to use \section{} and \subsection{} commands, these will automatically be printed on this slide as an overview of your presentation
\end{frame}

\input{joss.tex}

%\input{floss.tex}

\begin{frame}{Conclusion}

\begin{block}{Benefits \emoji{smiley}}
    \begin{itemize}
        \item JOSS is one opportunity to get credit for software development
        \item JOSS is a collaboration between author, editor and reviewers
    \end{itemize}
\end{block}

\begin{block}{Challenges \emoji{neutral-face}}
        \begin{itemize}
            \item  JOSS is funded by NumFocus, \emph{e.g.}\ server, DOI. However, all editors and reviewers are volunteers.
            \item Scalability! Last year 400 published papers means at least 800 reviewers. Do not burn our volunteers.
        \end{itemize}
\end{block}

 \emoji{pray} Please submit your software package and get credit for your work!\\
 \emoji{pray} Please sign up as reviewer to help JOSS to handle around 400 papers per year.


\tiny \doclicenseThis
\end{frame}

\end{document}


